TEMPERATURES AND METALLICITIES OF M DWARFS IN THE \apogee\ SURVEY

### 2019-07-31 paper/draft.tex
comment
change # sources

The spectra contain roughly 8000 pixels,
so we might expect the $\chi^2$ values to be close to 8000 in magnitude.
They are much higher.
This discrepancy flows from the fact that---while the spectral model is good at the percent
level---the signal-to-noise of the typical spectra are more than 100.
That is, the $\chi^2$ values do show that the model is not good in the frequentist
sense; it is only good at the percent level.
\color{gcolor}{This percent-level accuracy of the model in the data domain is also demonstrated...}\color{black} \\

@@

As a validation test of our derived temperatures, we perform a comparison between several color-temperature relations from literature, which use combination of \zmass\ and visual band photometries to predict temperatures (similarly to the \citealt{Schmidt:2016} evaluation of ASPCAP temperatures). To obtain visual band magnitudes for a set of sources, we cross-matched the 5,875 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,257 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:teff_comparisons} shows \cannon\ vs. photometric temperatures on the right, and ASPCAP vs. photometric temperatures on the left for each of the 6,257 sources, colored by their respective spectroscopic metallicities.

Compared to the \citealt{Mann:2015} and \citealt{Boyajian:2012} color-metallicity derived temperatures, both ASPCAP and \cannon\ temperatures show similar scatters of $\sim60\,$K, but offset by a constant.
We find \cannon\ to be in better agreement with \citealt{Mann:2015} and \citealt{Boyajian:2012}, with ASPCAP overestimating $\teff$ on average $\sim110-140\,$K, and \thecannon\ underestimating $\teff$ on average by $\sim10-20\,$K.

>>>>

The spectra contain roughly 8000 pixels,
so we might expect the $\chi^2$ values to be close to 8000 in magnitude.
They are much higher.
This discrepancy flows from the fact that---while the spectral model is good at the percent
level---the signal-to-noise of the typical spectra are more than 100.
That is, the $\chi^2$ values do show that the model is not good in the frequentist
sense; it is only good at the percent level.
% \color{gcolor}{This percent-level accuracy of the model in the data domain is also demonstrated...}\color{black} \\

@@

As a validation test of our derived temperatures, we perform a comparison between several color-temperature relations from literature, which use combination of \zmass\ and visual band photometries to predict temperatures (similarly to the \citealt{Schmidt:2016} evaluation of ASPCAP temperatures). To obtain visual band magnitudes for a set of sources, we cross-matched the 5,875 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 1,702 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:teff_comparisons} shows \cannon\ vs. photometric temperatures on the right, and ASPCAP vs. photometric temperatures on the left for each of the 1,702 sources, colored by their respective spectroscopic metallicities.

Compared to the \citealt{Mann:2015} and \citealt{Boyajian:2012} color-metallicity derived temperatures, both ASPCAP and \cannon\ temperatures show similar scatters of $\sim60\,$K, but offset by a constant.
We find \cannon\ to be in better agreement with \citealt{Mann:2015} and \citealt{Boyajian:2012}, with ASPCAP overestimating $\teff$ on average $\sim110-140\,$K, and \thecannon\ underestimating $\teff$ on average by $\sim10-20\,$K. \\
